
\section{General info}
Teacher: Natthew Greenberg
Office: MS 434 Monday wensday 11-12. (Can make appointments)

Assignments: Lyryx, available MS 317,MS515,MS521,MS571, AFC ,TFDL, and ES160. (Or pay for it)
Textbook: OpenText! (On D2L)

WWe will be going over the things in outline.pdf that's on dropbox.com/s/p4youx174kr1byz/outline.pdf
p4youx174kr1byz
	He tends to teach more in applications than theory.

\section{Review of matrix theory}

\subsection{Sustems of linear equations}
-Encoding systems into augmented matrix.
\begin{definition}[Reduced row echelon form]
All zero rows of $A$ are at the bottom.
Every nonzero row of $A$ has a leading 1.
A leading 1 is to the right of the leading ones in the rows above it.
A leading 1 is the only nonzero entry in its column.
\end{definition}
\begin{remark}
Reduced Row echelon form is great, as you can just see the asnwer and write it down.
\end{remark}
\begin{remark}[State of the system]
Solvable (unique) if no paramaters
Unsolvable when there is a row of zeros followed by a 1.
Solvable (infinite) if one or more paramaeters.
\end{remark}
\begin{definition}[Elementary row operations]
1 Interchange two rows of A.
Multiply a row of $A$ by a nonzero scalar.
Add a scalar multiple of one a of $A$ to a different row.
\end{definition}

\begin{theorem}
Every matrix is row equivalent to a unique matrix in RREF.
\end{theorem}

\begin{definition}[rank]
The rank of $A$ is written $\rank(A)$ is the number of nonzero rows in RREF of $A$.
\end{definition}

